Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-12-10 ms/response_JEB_20211024.txt

EDITOR. One other more minor point is that lack of evidence for spatial autocorrelation is not the same as evidence for a lack of spatial autocorrelation (indeed there is a reasonably strong, albeit not quite "significant" spatial correlation on Eleuthera), so some of the conclusions about a lack of isolation by distance and genetic drift should be toned down slightly.

(R) We changed the whole discussion paragraph on the effect of drift accordingly (new citations were added there), and also a sentence in the results to point out that Eleuthera had almost significant spatial correlation. We also toned down that statement in the abstract. Re-read this paragraph later on (it could benefit from info about the cruising range of an anolis). Note that the citations have been updated, with new ones accompanying the requested changes by the reviewers.

EDITOR. How similar are the habitats between islands or could differences in habitat between islands explain some of the variation between islands?

(R) We do not have these data unfortunately (do we not? ask Colin).

REVIEWER1. Do you know whether such colour variation nicely described by your analyses, is actually detectable by conspecific, congeners and/or predators, the “agents” of selection?  For instance, do you think all dewlaps will be similarly seen under similar light/background conditions? Or whether observers can tell apart dewlaps coming from different habitats? In the first case, it is likely that the non-directional variation that you describe is not under selection, as to observers’ eyes, all dewlap colours look similar. In the second case, the conclusions will be similar to the ones you get with your current approach. This question can be tested applying vision modelling using your reflectance profiles, and an irradiance profile of at least one of the habitats that you studied. Perhaps this has been already done in other studies. If such is the case, you can clearly mention it.

(R) We do not know how detectable the reported differences in coloration are. Indeed, to know this we would need to do some visual modelling, and for this we would also need some habitat irradiance data, which we do not have unfortunately. Visual modelling has been performed in Anolis lizards, but to the best of our knowledge it has not been done on our study populations, and so we do not know if the lizards can detect the differences in coloration of conspecifics from different habitats. Maybe a discussion paragraph about that?

REVIEWER1. Among the differences that can be found on the three studied habitats, authors mostly talk about differences in light incidence. Are there any differences also in background colour? Predator community? Anole community? If so, how will they contribute or not to the obtained results?

(R) Background color definitely varies between habitats, which can be seen with the naked eye from photos, but we did not quantify this precisely (we do not have irradiance profiles for the habitats telling us which wavelengths are different). Anole and predator communities have been shown to vary between islands (at least in density of the main species, which are overall present across all islands), but we do not know whether they also vary between the habitats within islands.

REVIEWER1. How big is the home range of an Anolis? Sorry of I missed it. This information will help understanding the importance of your experimental design

(R) Ambika's paper reports wider territories than previously thought in A. sagrei: 225m2 for males (which is 15 by 15m), and 36m2 for females (6 by 6m), with with evidence for multiple matings in both sexes. These estimates were measured on a campus in Florida and may not represent the real territory size on our study islands, however. Nevertheless, although the species is still classified as territorial, its ability for movement and promiscuity, its continuous distribution at high densities throughout the islands and the polyphyly of individuals from different habitats within islands suggests that long-range gene flow is highly plausible. (Maybe the guys will know something about the cruising range of an anolis...)

REVIEWER1. In line 91, what do you mean by climatic variables? Light incidence?

(R) We have now precised that these climatic variables include precipitations and solar incidence, among others, and those were interpreted as causing differences in types of habitat, with different light environments, among islands.

REVIEWER1. In line 413, perhaps is worth it including a short definition of runaway sexual selection.

(R) This is now clarified.

REVIEWER2. Of course, also the size and use of the dewlap is essential during signalling (see e.g. papers by Lailvaux, Irschick, Vanhooydonck, Driessens, Husak, Baeckens, to name a few). While I understand this is not the goal of the study, I think it’s still important to invest a couple of sentences or a short paragraph on how other characteristics of the dewlap (aside from colouration) are important too, and that those characteristics (possibly interaction with colouration) might vary within- and among-islands as well.

(R) We have modified the second-to-last paragraph to mention those other facets of anole display behavior, and added new references to back them up.

### 2021-12-10 ms/sections/abstract.tex
answered reviewer comments

Animal signals evolve in an ecological context. Locally adapting animal sexual signals can be especially important for initiating or reinforcing reproductive isolation during the early stages of speciation. Previous studies have demonstrated that dewlap color in \textit{Anolis} lizards can be highly variable between populations in relation to both biotic and abiotic adaptive drivers at relatively large geographical scales. Here, we investigated differentiation of dewlap coloration among habitat-types at a small spatial scale, within multiple islands of the West Indies, to test the hypothesis that similar local adaptive processes occur over smaller spatial scales. We explored variation in dewlap coloration in the most widespread species of anole, \textit{Anolis sagrei}, across three characteristic habitats spanning the Bahamas and the Cayman Islands, namely beach scrub, primary coppice forest and mangrove forest. Using reflectance spectrometry paired with supervised machine learning, we found significant differences in spectral properties of the dewlap between habitats within small islands, sometimes over very short distances. Passive divergence in dewlap phenotype associated with isolation-by-distance did not explain our results. On the other hand, these habitat-specific dewlap differences varied in magnitude and direction across islands, and thus our primary test for adaptation -- parallel responses across islands -- was not supported. We suggest that neutral processes or selection could be involved in several ways, including sexual selection. Our results shed new light on the scale at which signal color polymorphism can be maintained in the presence of gene flow, and the relative role of local adaptation and other processes in driving these patterns.

>>>>

Animal signals evolve in an ecological context. Locally adapting animal sexual signals can be especially important for initiating or reinforcing reproductive isolation during the early stages of speciation. Previous studies have demonstrated that dewlap color in \textit{Anolis} lizards can be highly variable between populations in relation to both biotic and abiotic adaptive drivers at relatively large geographical scales. Here, we investigated differentiation of dewlap coloration among habitat types at a small spatial scale, within multiple islands of the West Indies, to test the hypothesis that similar local adaptive processes occur over smaller spatial scales. We explored variation in dewlap coloration in the most widespread species of anole, \textit{Anolis sagrei}, across three characteristic habitats spanning the Bahamas and the Cayman Islands, namely beach scrub, primary coppice forest and mangrove forest. Using reflectance spectrometry paired with supervised machine learning, we found significant differences in spectral properties of the dewlap between habitats within small islands, sometimes over very short distances. Passive divergence in dewlap phenotype associated with isolation-by-distance did not \textcolor{olive}{seem to} explain our results. On the other hand, these habitat-specific dewlap differences varied in magnitude and direction across islands, and thus our primary test for adaptation -- parallel responses across islands -- was not supported. We suggest that neutral processes or selection could be involved in several ways, including sexual selection. Our results shed new light on the scale at which signal color polymorphism can be maintained in the presence of gene flow, and the relative role of local adaptation and other processes in driving these patterns.

### 2021-12-10 ms/sections/discussion.tex
answered reviewer comments

\paragraph{Dewlap coloration differs between habitats, but the differentiation is inconsistent with adaptive convergence} Dewlaps are highly conspicuous in anoles and used as communication signals in courtship \citep{Sigmund1983, Driessens2014, Driessens2015} and territorial displays \citep{Losos1985, Macedonia1994, Macedonia2013}. On five of the nine islands we sampled in the West Indies, we found that \textit{A. sagrei} male dewlap coloration significantly varied between individuals living in three different habitat types  (beach scrub bush, primary coppice forest and mangrove forest), even though those habitats were in close proximity to each other and the \textit{sagrei} populations are continuously distributed between the habitats.\\

One compelling indicator of adaptation by natural selection is the repetition of patterns of differentiation across localities \citep{Losos2009, Losos2011}. In the context of this study, had we found consistent patterns of dewlap differentiation between habitats, we would have concluded that there was likely an adaptive basis for this pattern. However, the inconsistent and idiosyncratic patterns of dewlap variation we observed contradict this prediction. What then explains the observed differences among the populations?\\

One explanation is that this pattern is the result of multiple island colonizations of phenotypically different individuals to these habitats. However, we reject this possibility because all of the island populations in this study are strictly monophyletic, reflecting a single colonization event per island (van de Schoot, unpublished thesis; \citealt{Driessens2017, Reynolds2020}). Other drivers could be at work, including genetic drift, phenotypic plasticity, and divergent natural selection. Of these, we find divergent natural selection the most likely explanation, suggesting that future research with additional granularity on the drivers of dewlap coloration is needed.

\paragraph{A role of neutral drift is unlikely} Genetic drift may lead to patterns of trait divergence similar to local adaptation \citep{Miles2019}. We think this scenario is implausible, however, as we found significant differences in dewlap color over distances too small for genetic drift to have realistically counteracted the effect of homogenizing gene flow \citep{Richardson2014}. On Bimini, for example, we detected differences between sites only a few hundred meters away and \textit{A. sagrei}, have previously been shown to be highly mobile \citep{Kamath2018}. Moreover, habitat-populations within each island were found to be non-monophyletic and often share identical haplotypes, based on phylogenetic analysis of mitochondrial DNA (van de Schoot et al. unpublished thesis). This is further evidence of gene flow between habitats.\\

It is possible that complex drift scenarios other than simple distance-mediated, diffusion-like processes may be at play \citep{Miles2019}. For example,  we did detect a significant signal of isolation-by-distance on Eleuthera, without finding differences in dewlap coloration between habitats, suggesting a possible role of drift on this island. Nonetheless, by and large our results align with previously documented cases of highly localized  dewlap color divergence despite gene flow in multiple species of anoles. \citet{Ng2012} and \citet{Ng2016} found divergent dewlap coloration despite gene flow between subspecies of \textit{A. distichus} on Hispaniola, and proposed this as a mechanism of reproductive isolation in the early stages of speciation \citep{Ng2011, Lambert2013, Ng2017}. \citet{Stapley2011} found that dewlap color polymorphism was maintained in the absence of genetic structure between populations of \textit{A. apletophallus} from Panama. \citet{Thorpe2002a} found that divergence in dewlap coloration matched habitat-type better than mitochondrial lineage in \textit{A. roquet} on Martinique, and a convergent pattern was found in \textit{A. trinitatis} on the featureless island of St Vincent \citep{Thorpe2002b}. Finally, regionally-distinct body coloration, but not dewlap coloration, is present in \textit{A. conspersus} on another small island, Grand Cayman, where no physical barriers to gene flow exist \citep{Macedonia2001}.

\paragraph{A role of phenotypic plasticity is unlikely} Differences in coloration between habitat populations may not be genetically determined and instead may be influenced by environmental factors. The yellow, orange and red coloration in anoline dewlaps are produced by pterins and carotenoids \citep{Ortiz1962, Ortiz1962a, Ortiz1963, Ortiz1966, Macedonia2000, Steffen2007, Steffen2009}. Animals lack the ability to synthesize carotenoids, and those must therefore be found in the diet, while pterins are synthesized from nucleotides \citep{Goodwin1984, Hill2002, Hill2006}. However, experimental manipulation of dietary carotenoid content showed no effect on dewlap coloration in \textit{A. sagrei} \citep{Steffen2010} nor in \textit{A. distichus} \citep{Ng2013}, which also has an orange-based dewlap. (Dewlap color has also been shown to change in relation to parasite load \citep{Cook2013}, though parasites were not investigated in this study. -- to remove) These laboratory results  suggest a plastic response in dewlap color to differences in diet across habitats unlikely, suggesting the differences we observed could therefore be genetically based. This hypothesis is further supported by \citet{Cox2017}, who found a high degree of heritability of dewlap coloration in \textit{A. sagrei}.

\paragraph{Sensory Drive - maybe drop?} One hypothesis that a relationship would exist between dewlap color and habitat stems from the idea that the communication signals evolve adaptively in response to light environment (the sensory drive hypothesis, \citealt{Endler1988, Endler1992, Endler1998}). However, we find this explanation unlikely because the differences we observed were both inconsistent among islands and inconsistent with predictions of the sensory drive hypothesis. Previous studies have proposed that dewlap coloration may have evolved to be maximally detectable under local light conditions, primarily through UV contrast (i.e. UV-brighter dewlaps in UV-dark, mesic habitats and UV-darker dewlaps in UV-bright, xeric habitats), in \textit{ A. cristatellus} and \textit{A. cooki} from Puerto Rico \citep{Leal2002, Leal2004}. On the contrary, we found no apparent habitat-dependent maximization of UV-contrast, or just any contrast in \textit{ A. sagrei}. Instead, we found for example the darkest dewlaps in the dark, mesic habitat -- primary coppice forest -- on three islands, and dewlaps often differed the most between beach scrub and mangrove forest, two xeric habitats with similar, high irradiance levels \citep{Howard1950, Schoener1968}. Studies of Jamaican and Hispaniolan anoles similarly found between-habitat differences in dewlap coloration but no evidence for higher dewlap detectability in different habitats \citep{Fleishman2009, Ng2012}. Our data are consistent with those previous results in suggesting that adaptation to local light conditions, or at least broad habitat types, is not a major driver of the within-island variation in dewlap coloration in \textit{A. sagrei}.

\paragraph{Fisherian sexual selection - maybe drop?} Selection, however, needs not necessarily be linked to habitat type, and may take the form of arbitrary, "Fisherian" sexual selection, where female preferences differ between localities for reasons unrelated to the environment, driving the divergent evolution of male ornaments \citep{Lande1981, Andersson1994, Higashi1999}. This process could account for the idiosyncratic patterns of within-island divergence we report, where initial differences in female preferences could have arisen for nonselective reasons (e.g. plasticity or random drift). Substantial levels of promiscuity in \textit{A. sagrei} suggest ample opportunity for female mate choice \citep{Kamath2018}, and are in line with this scenario. However, \citep{Baeckens2018} found no link between \textit{A. sagrei} dewlap coloration and size dimorphism (a proxy for sexual selection) in an among-island study of the same archipelagos.

\paragraph{Natural selection may proceed differently across islands and habitats} A further potential explanation for the inconsistencies in dewlap coloration among habitats between islands is that the observed differences in dewlap color are the result of divergent natural selection. If that is the case, however, either the habitats we have identified are not as similar as we thought, such that the same habitat type on different islands favors different colors, or, alternatively, the selective pressures causing dewlap divergence are related to some environmental factor other than habitat type that we did not measure. The habitats on different islands may, for example, differ in densities of predators or congeners, which have been shown to affect among-island dewlap diversity \cite{Vanhooydonck2009, Baeckens2018}. In particular, \citet{Baeckens2018} recently showed that dewlaps with spotted patterns occurred more often in \textit{A. sagrei} on islands with more coexisting species of anoles. Therefore, if local adaptation occurs, it may be more likely to involve components of the environment that do not encompass our broad habitat categories leading to island-specific differences between habitats rather than parallel differences expected if habitat identity was the primary selective pressure driving divergence.\\

One last possibility to explain idiosyncratic patterns of between-habitat differences we observe is that, if island populations are different in color on average, they may be experiencing different portions of a within-island fitness landscape whose shape changes depending on the starting phenotype. In this study, we indeed found that dewlap coloration differed much more between than within islands. So, a population may not respond to selection in the same manner depending on its starting conditions. This is true not only in terms of phenotype (average dewlap color differs among islands) but also genetic composition (e.g. independent colonizations may have important genetic founder effects, \citealt{Reynolds2020}), and so the selective pressures applying to populations with different starting phenotypes may drive these divergent outcomes. For example, \citet{Fleishman2020} found that yellow stimuli are less detectable than red stimuli in high-light environments while both colors are readily detectable in low-light environments. Consequently, the environmental pressures applying to yellower dewlaps may differ than those for redder dewlaps, as red dewlaps should be always equally or more detectable than yellow dewlaps across light environments, whereas yellow dewlaps could experience more directional selection towards more red when in a high-light environments.

\paragraph{Conclusion} We identified patterns of dewlap color differentiation in populations of \textit{A. sagrei} from different habitat-types on multiple small islands of the West Indies. However, our main hypothesis to explain our findings -- local adaptation and sensory drive -- received little support from our multiple-island dataset. We also found other mechanisms such as drift or plasticity unlikely candidates to explain the observed patterns. This suggests that combinations of multiple factors interacting in subtle ways, and not necessarily in parallel across islands, may have contributed to present-day dewlap color diversity.

>>>>

Two main insights follow from our results. First, we detected significant differences in dewlap coloration between habitats within seven out of the nine islands investigated (excluding North Andros where the follow-up univariate analyses were not significant), suggesting a putatively high potential for local differentiation of dewlap coloration in \textit{Anolis sagrei}. Second, we found differences in coloration along different dimensions of color space, and in different directions, on different islands.\\

Detectable differences in dewlap color between populations are surprising, as habitats were often in close geographical proximity to each other (as close as a few hundred meters on Bimini and most of the time within ten kilometers). Indeed, given that (1) the populations were continuously distributed between the habitats, (2) populations from different habitats were not monophyletic with respect to mitochondrial haplotypes (\citealt{vandeSchoot2016} unpublished thesis), and (3) \textit{A. sagrei} is highly mobile \citep{Kamath2018}, we would have expected more homogeneous distributions of color phenotypes within islands due to gene flow, with fewer differences between populations, especially those in close proximity.\\

Several scenarios could account for these findings. One explanation is an adaptive one: populations living in different habitats could be phenotypically adapted to their local environmental conditions. Given that the brightly colored dewlap of \textit{A. sagrei} is used as a communication signal, its color may be a target for selection if the transmission or perception of the signal differs from one habitat to another, for example because of differences in ambient light, according to the sensory-drive hypothesis \citep{Endler1988, Endler1992, Endler1998}. The sensory-drive hypothesis has been tested multiple times for dewlap coloration in \textit{Anolis} lizards, with mixed results. Some authors found support for it \citep{Leal2002, Leal2004}, while others found differences in dewlap coloration between habitats inconsistent with the sensory-drive hypothesis \citep{Fleishman2009, Ng2012}.\\

If our results were an example of sensory drive, we would have expected to see consistent differences between populations from different habitats across islands, given the apparent environmental consistency each of the three habitat types across the islands we sampled. In particular, we would have expected divergence in line with increased detectability given local light conditions, such as the high contrasts with background vegetation found in the UV range in \citet{Leal2002} and \citet{Leal2004}. We might also have expected mangrove and beach scrub lizards, both inhabiting areas with high light penetration, to have more similar dewlaps, and to differ significantly from lizards from the coppice habitat, where irradiance is low. Instead, we found inconsistencies in the way dewlap color differed between habitats across islands. While short-wavelengths (UV reflectance) were often involved in color differences, they were not involved on all islands where significant differences were detected. On some islands, other or additional variables differed, such as brightness, red reflectance or the reflectance at the ends of the spectrum visible to \textit{Anolis} lizards (UV and red, \citealt{Lazareva2012}) relative to intermediate wavelengths (blue-to-yellow). Similar portions of the spectrum were sometimes involved in opposite directions on different islands, such as on Abaco and Cayman Brac, where mangrove lizards had a higher UV-reflectance than beach scrub lizards on the former, but a lower UV-reflectance on the latter. Overall, the observed heterogeneity of divergence patterns across islands provides no support to a sensory-drive explanation.\\

It is presently not known if the reported differences in coloration have a genetic basis. Yet, we find it unlikely that these differences arose through phenotypic plasticity, as although the carotenoids that partly make up the red and orange colors of anole dewlaps must be found in the diet \citep{Goodwin1984, Hill2002, Hill2006}, studies testing the effect of carotenoid deprivation \citep{Steffen2010, Ng2013} and heritability \citep{Cox2017} of dewlap coloration in \textit{A. sagrei} and \textit{A. distichus} (another species with a carotenoid-based dewlap), found little support for phenotypic and developmental plasticity in dewlap coloration. One exception is a study demonstrating that lizards heavily parasitized by skin mites had duller dewlaps \citep{Cook2013}, but we found no sign of that in our study.\\

\sout{We found no evidence for a role of genetic drift in explaining the observed patterns either. First, \textit{A. sagrei} was distributed across the islands continuously, usually at relatively high population densities, rather than in small and isolated populations where drift might be expected to have a strong effect. Second, we found no evidence of isolation-by-distance except on Abaco, which was sampled at the largest geographical scale, with sites nearly a hundred kilometers apart from each other. Hence, while isolation-by-distance may explain long-range differences on this island, most of the differences among habitats across the rest of the sampling region are unlikely to be explained by genetic drift, as habitats were often in close proximity (less than 10km).}\\

\textcolor{olive}{Genetic drift may contribute to some of the observed variation. Indeed, while only Abaco showed significant patterns consistent with isolation-by-distance (which may emerge under limited dispersal and drift, \citealt{Wright1943, Kimura1964, Slatkin1987}), there may have been too few sites on most islands to conclusively detect it, and even then, the absence of detectable isolation-by-distance may not necessarily constitute evidence for the absence of drift. Besides, spatial autocorrelation was the strongest on islands sampled at the largest scales (e.g. some sites on Abaco were nearly 100km apart, and Eleuthera -- the second strongest signal, albeit nonsignificant -- had sites more than 30km apart), such that it is possible that neutral processes and/or dispersal limitations might in fact contribute to shaping variation over long distances. That said, many significant differences were found between habitats in close proximity, contrary to what would be expected under isolation-by-distance, including on islands where spatial autocorrelation was detected. Moreover, \textit{A. sagrei} was distributed across the islands continuously, usually at relatively high population densities, rather than in small and isolated populations particularly prone to drift. Together with the fact that isolation-by-distance may not necessarily only emerge from drift (e.g. if there is a spatial environmental gradient), this indicates that genetic drift may have limited potential to explain the differences observed between habitats, at least at a local scale.}\\

In this study, we found larger differences among than within islands, a pattern already reported and linked to climatic conditions \citep{Driessens2017} and to densities of predators and of anole congeners \citep{Vanhooydonck2009, Baeckens2018}. Differences among habitats within islands, however, are still difficult to account for. Remaining hypotheses may include, for example, runaway sexual selection \textcolor{olive}{(i.e. arbitrary preferences of females for some colors over others, \citealt{Andersson1994})} \sout{arbitrarily} operating in different directions across islands, but no evidence so far suggests that dewlap is a target of mate choice in anoles \citep{Tokarz2002, Tokarz2005, Lailvaux2006, Nicholson2007}. Another hypothesis is that the different genetic constitutions of different islands, perhaps resulting from founder effects (the islands have been colonized independently, \citealt{vandeSchoot2016} unpubl.; \citealt{Driessens2017, Reynolds2020}), may have predisposed populations to adapt differently to similarly selective circumstances. \textcolor{olive}{That said, signalling can be a multifacetted behavior, and while we focused on dewlap color here, other potentially important elements of behavioral interactions include dewlap size, dewlap patterning, display activity as well as behaviors associated with dewlap extensions such as headbobs and pushups \citep{Vanhooydonck2005, Driessens2014, Driessens2015, Lailvaux2015}. These have been linked in various ways (and not always consistently across studies) not only with environmental variables but also with proxies for sexual selection, predation and species recognition \citep{Vanhooydonck2005, Lailvaux2007, Vanhooydonck2009, Driessens2017, Baeckens2018}, which do vary among islands but may also vary within islands, and possibly in interaction with dewlap color.} Either way, new data would be needed to test these hypotheses.\\

Altogether, our results show that dewlap color of \textit{A. sagrei} commonly varies between habitat types, even in close geographical proximity, within islands of the West Indies. However, coloration differs in different ways across similar habitats from one island to another. We discussed several non-mutually exclusive mechanisms that could explain these observations. Nevertheless, heterogeneous patterns of divergence across islands do not support an adaptive sensory-drive scenario, and we propose that within-island dewlap color variation may be underlain by a more subtle mosaic of factors.

### 2021-12-10 ms/sections/introduction.tex
answered reviewer comments

% Animal signals may be shaped by their environment

@@

% One main barrier to the maintenance of diversity is gene flow

@@

\textit{Anolis sagrei} is widespread across islands of the West Indies \citep{Reynolds2020}. It has been the subject of numerous studies concerning local adaptation \citep{Losos1994, Losos1997a, Losos2001, Kolbe2012}, biological invasion \citep{Kolbe2008}, and sexual selection \citep{Tokarz2002, Tokarz2005, Tokarz2006, Driessens2014, Steffen2014, Driessens2015} among many other topics. Between-island variation in the mainly orange-red color of its dewlap was shown to be better explained by climatic variables \citep{Driessens2017} than by proxies for biotic factors such as sexual selection or predation pressure \citep{Vanhooydonck2009, Baeckens2018}. How intra-island differences in habitat may contribute to the diversity of dewlap coloration, however, remains unexplored, and may reveal new insights into the scale of local differentiation despite gene flow.\\

% What we did

@@

% Jonathan does not like when we sum up the results at the end of the intro

% We found strong support for fine-scale, within-island differences in coloration between lizards inhabiting the three habitat-types in several color space dimensions, suggesting a potentially strong effect of divergent selection. However, the divergence patterns we observed did not match our \textit{a priori} predictions and were inconsistent between islands. We found no evidence of isolation-by-distance as an explanation for the observed differences. Our results are nevertheless consistent with small-scale adaptive maintenance of signal polymorphism despite presumed considerable opportunity for gene flow, and might suggest that idiosyncracies of local drift, selection, and gene flow contribute to differing outcomes in different populations.

% Bibliography notes:

% Anolis sagrei was shown to be able to rapidly invade available ecological niches upon colonization of new islands through changes in limb proportions (Losos1997a; Losos2001)

% Convergence

% Besides, \textit{Anolis} lizards are well-known examples of eco-morphological evolutionary convergence, where multiple ``ecomorphs'' adapted independently, but in similar ways, to similar ecological niches across islands of the Greater Antilles (Losos2004; Losos2009). This extent of evolutionary determinism seems to act within species at present too. Populations of \textit{A. sagrei} were shown to undergo the same eco-morphological divergence upon colonization of new islands as ecomorphs did millions of years before (Losos1997a; Losos2001; Calsbeek2007; Losos2007). Strong developmental constraints on morphology seem to explain this tendency (Sanger2012; McGlothlin2018). However, despite the evidence suggesting potential for evolutionary convergence at the intra-specific level in anoles, this pattern is unknown for communication signals such as dewlap coloration. Populations of a same species, because they share a common genetic architecture, are expected to evolve convergent adaptations more often than distantly related species (Ord2015), and this could apply to the dewlap of \textit{A. sagrei}. On the other hand, sexual signals are often evolutionarily labile due to sexual selection (Kraaijeveld2011), but also selection mediated by other recipients of the signal (Endler1981; Endler1988; Endler1984; Endler1993; Endler1993a; Endler1998). This is consistent with the high diversity of dewlaps across anole species (Nicholson2007) and could imply evolutionary contingency for this colorful trait.\\

>>>>

@@

@@

\textit{Anolis sagrei} is widespread across islands of the West Indies \citep{Reynolds2020}. It has been the subject of numerous studies concerning local adaptation \citep{Losos1994, Losos1997a, Losos2001, Kolbe2012}, biological invasion \citep{Kolbe2008}, and sexual selection \citep{Tokarz2002, Tokarz2005, Tokarz2006, Driessens2014, Steffen2014, Driessens2015} among many other topics. Between-island variation in the mainly orange-red color of its dewlap was shown to be better explained by climatic variables \textcolor{olive}{such as annual precipitation and solar radiation (proposed to affect the average vegetation type on each island and among other things, its ambient light environment, \citealt{Driessens2017})},  than by proxies for biotic factors such as sexual selection or predation pressure \citep{Vanhooydonck2009, Baeckens2018}. How intra-island differences in habitat may contribute to the diversity of dewlap coloration, however, remains unexplored, and may reveal new insights into the scale of local differentiation despite gene flow.\\

@@
